Analysis of Odd one out experiment

### 2020-02-21 reports/odd_one_out/analysis_oddoneout.Rmd
working on oddoneout experiment - combination of metrics

metrics <- readRDS(file = here("data", "oddoneout", "metrics_190614.rds"))

wrong_trials <- df %>% select(prot_id_version,trial_id,im1:im9) %>% group_by(prot_id_version,trial_id) %>% gather("key", "value",im1:im9) %>% summarize(n = length(unique(value))) %>% filter(n<9) %>% select(-n)

@@

@@

```{r metrics results}
p <- metrics %>% 
  filter(metric!= "ssim_correct" & metric!= "correct") %>% 
  ggplot(aes(x = quintile, y = value_fc7, col = metric, group = metric)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  theme(aspect.ratio = 1) +
  coord_cartesian(ylim = c(0,0.5)) +
  geom_hline(yintercept = 1/9) +
  ylab("Perc. correct") +
  scale_x_continuous("Quintile", breaks = c(2,3,4), labels = c("2","3","4")) +
  theme(text = element_text(size=18)) + scale_color_manual(labels = c("GIST", "HOG", "RGB", "SIFT"), values = c("#E41A1C","#377EB8","#4DAF4A","#984EA3")) + 
  stat_summary(fun.y=mean, geom="line") +
  ggtitle("Predict CNN")
  #theme(legend.justification = c(1,1), legend.position=c(0.99,0.99))
p
ggsave(file.path(plots_dir, "Fig_chp3_metrics_explanation_fc7.svg"), p, width = 6, height = 6)

@@

>>>>

metrics <- readRDS(file = here("data", "oddoneout", "metrics_190614.rds"))
metrics_wide <- readRDS(file = here("data", "oddoneout", "metrics_wide_190614.rds"))
wrong_trials <- df %>% select(prot_id_version,trial_id,im1:im9) %>% group_by(prot_id_version,trial_id) %>% gather("key", "value",im1:im9) %>% summarize(n = length(unique(value))) %>% filter(n<9) %>% select(-n)

@@

# Correlation of metrics

```{r}
df_metrics %>% select(ssim, hog, gist, sift_sum,pdistRGB) %>%  cor()
```

@@

```{r metrics results}
p <- metrics %>% 
  filter(metric!= "ssim_correct" & metric!= "correct") %>% 
  ggplot(aes(x = quintile, y = value_fc7, col = metric, group = metric)) + 
  stat_summary(fun.data = "mean_cl_boot", position = position_jitter(0.2)) + 
  theme(aspect.ratio = 1) +
  coord_cartesian(ylim = c(0,0.5)) +
  geom_hline(yintercept = 1/9) +
  ylab("Perc. correct") +
  scale_x_continuous("Quintile", breaks = c(2,3,4), labels = c("2","3","4")) +
  theme(text = element_text(size=18)) + scale_color_manual(labels = c("GIST", "HOG", "RGB", "SIFT"), values = c("#E41A1C","#377EB8","#4DAF4A","#984EA3")) + 
  stat_summary(fun.y=mean, geom="line") +
  ggtitle("Predict CNN")
  #theme(legend.justification = c(1,1), legend.position=c(0.99,0.99))
p
ggsave(file.path(plots_dir, "Fig_chp3_metrics_explanation_fc7.svg"), p, width = 6, height = 6)

@@

### Combine metrics

```{r combine metrics}
metrics_wide %>% 
  mutate(metrics_combined = max(ssim_correct,hog_correct,gist_correct,sift_correct)) %>% 
  ggplot(aes(x = quintile, y = value_partic, col = metric, group = metric))
